\chapter{Complex Numbers}
\section{intro}
When simply using real numbers, you cannot always get the right answer to a given equation. An example of this could be the equation $x^2=-1$. Therefore sometimes we have to use a different number system, which uses the number $i$. 
\begin{align*}
i=sqrt(-1)
\end{align*}
When squarred the number $i$ becomes:
\begin{align*}
i^2=-1
\end{align*}
With to the third:
\begin{align*}
i^3=-i
\end{align*}
and to the fourth:
\begin{align*}
i^4=1
\end{align*}
These first four of $i$ creates a loop. $i$ to the fifth will therefore be the same as $i$ to the first, $i$ to the seventh is the same as $i$ to the third \\
By using this complex numbers, you can create infinitely more numbers.  
An example of this is the numbers: $2i$ and $-7i$, these are called pure imaginary numbers. When writing pure imaginary numbers you use the form $bi$, where $b$ is a real number that is not $0$. \\
If you put another part on these imaginary number, thus $a+bi$ you get the complex numbers. Example $3+4i$ and $-12i+6$. In this case $a$ is the real part and $b$, where $i$ is, is the imaginary part. $a$ and $b$ are real numbers. By using this method you can make all pure imaginary numbers into a complex number by writing it like this: $0+3i$. $3i$ does not stand alone anymore and is therefore a complex number now. You can also rewrite every real number into a complex by doing this $2+0i$. \\
By using complex numbers you can therefore find a solution to any given polynomial equation. \\ 
When plotting complex numbers you use the complex plane. The axes are different from the normal coordinate system, instead of the normal x and y-axes, you instead have the real part and the imaginary part as the axes. An example of this is shown on the picture below.
\section{Adding and subtracting}
The rules of addition are much like the rules of simply adding two variables of the same type together. For instance, if you have something like $(5+2i)+(9+8i)$ then you can add the complex numbers and the constants and put it together on the general form; $a+bi$. In this case, we get $14+10i$. 
\\
Subtracting is similar because you can only subtract a complex number from another complex number, and the same goes to the constants. Here is an example: \\
\begin{align*}
(21 + 3i) - (2 - 2i) = 21 + 3i - 2 + 2i = 19 + 5i
\end{align*}
From the examples above we can see that subtracting and adding with complex numbers is identical to subtracting and adding other and more familiar variables such as (x, y so on).
\section{Multiplying}
When multiplying with complex numbers it can get a little different than multiplying with other variables, as $i=sqrt(-1)$ , $i^2=-1$ , $i^3=-i$ , $i^4=1$. So if we take an example: \\
\begin{align*}
(3+5i)(4-3i) = 12 - 9i + 20i - 15i^2 = 12 + 11i - 15 \cdot (-1) = 27 + 11i
\end{align*}
The difference is when $x$ is multiplied by $x$ the result is $x^2$, but since there is a definition for $i^2=-1$ the procedure is slightly different.
\section{Dividing}
When dividing with a complex number the aim is to get some values we can put on the general form $a + bi$. Here is an example: \\
\begin{align*}
\frac{18 + 10i}{3 + 2i} =\frac{(18 + 10i)(3 - 2i)}{(3+2i)(3-2i)} =\frac{54 - 36i + 30i - 20i^2}{9 - 9i^2} =\frac{54 - 6i - 20 \cdot (-1)}{9 - 9 \cdot (-1)} =\frac{74 - 6i}{9 + 9} =\frac{74}{18} - \frac{6}{18}i =\frac{37}{9} - \frac{1}{3}i
\end{align*}